Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-28 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

% Hier jetzt noch den Abschnitt über Bednarska2020 einfügen (anderer PC)

@@

The delivery of fluorescently labeled molecules with the nanopipette could be also used for 
combining it with single-molecule diffusion investigations \cite{Bruckbauer2007, Bruckbauer2010}. 
In both studies the scanning ion conductance microscope was combined with total internal 
reflection fluorescence (TIRF) investigations and the diffusion of single molecules over different 
regions at a spermatozoa were investigated.

>>>>

In a study investigating the formation of human immunodeficiency virus (HIV) VLPs the correlated
SICM-fluorescence confocal microscopy (SICM-FCM) was used to investigate topography changes
together with die distribution of fluorescently labeled viral proteins like Gag or Viral Protein R 
(Vpr) \cite{Bednarska2020}. In contrast of investigating the virus formation with total internal 
reflection fluorescence (TIRF) microscopy \cite{Jouvenet2008} the upside (Oberseite?) of the cells 
were investigated. The release of VLPs from the upside can be a lot faster, than the release times 
that were known from TIRF measurements and difference between different cell types and labeled 
virus proteins were found \cite{Bednarska2020}.

@@

The delivery of fluorescently labeled molecules with the nanopipette could be also used for 
combining it with single-molecule diffusion investigations \cite{Bruckbauer2007, Bruckbauer2010}. 
In both studies the scanning ion conductance microscope was combined with TIRF investigations and 
the diffusion of single molecules over different regions at a spermatozoa were investigated.
